Bioverse: Origins of Life

### 2023-10-03 src/tex/ms.tex
add a note
describe modeling of H3 (NUV correlation)

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on a planet with a minimum past UV flux.
Here, we focus on the prebiotically interesting \SIrange{200}{280}{\nano\meter} range CITE and the quiescent stellar flux.  %~\citep{RanjanSasselov2016}.
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received UV radiation in this wavelength range that exceeded a minimum NUV flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for $\geq \SI{100}{\mega\year}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
We assign the development of life to a fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\subsection{Habitable Worlds Observatory}
\subsubsection{target list}
\todo[inline]{Provisional stellar target List for the habitable Worlds Observatory:~\citep{Mamajek2023}}

@@

>>>>

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting NUV range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary habitable zone during this entire period.

For each exo-earth candidate, we interpolated the age- and stellar mass-dependent habitable zone fluxes obtained by \citet{Richey-Yowell2023} and computed the evolution of the inner (runaway greenhouse) and outer (maximum greenhouse) edges as a function of planet mass, stellar spectral type using the results of \citet{Kopparapu2014} and the stellar luminosity evolution of \citet{Baraffe1998}.
We then determined which planets were both in the HZ and had NUV fluxes above $F_\mathrm{NUV, min}$ for $\Delta T_\mathrm{min} \geq \SI{100}{\mega\year}$.
We assigned the development of life to a fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \,\mathrm{and\, in\, HZ} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\subsection{Habitable Worlds Observatory}
\subsubsection{target list}
\todo[inline]{Provisional stellar target List for the habitable Worlds Observatory:~\citep{Mamajek2023}} % read like in https://github.com/mkenworthy/HWObows/tree/40b1e5f2bc2bbbe8c999b097c80ca5a8cda0aeae/src/scripts

@@

\subsection{Contextual support for potential biosignature detections}
\todo[inline]{discuss how planetary context may impact credibility of tentative biosignature detections (e.g., if there is a good fit with a predicted OOL pattern; or the opposite: the planetary context does not fit well to any OOL scenarios)}
